This is the title [Article v\versionnumber]

### 2022-09-08 manuscript/manuscript.tex
Update manuscript.tex

Double-counting is accounted in two different ways. The first method uses the water-displacement method. This method is applicable when determining the energetic cost of kicking out a water molecule. For example, when a ligand binds to the protein, water molecules will be displaced from the binding pocket to
the bulk.

\begin{equation}
	\Delta E^R_\textit{ww} = n^\textit{R} E^\textit{bulk}_\textit{ww} - E^\textit{R,corr}_\textit{ww}
\end{equation}

@@

\begin{equation}
	\Delta E^\textit{R,norm}_\textit{ww} = E^\textit{R,norm}_\textit{ww} - 2E^\textit{bulk}_\textit{ww}
\end{equation}

>>>>

\todo The double counting is accounted for by divinding the Eww by 2. It's done in the code
\todo postprocessing user can multiply it by 2

@@
